Are populations like a circuit? The relationship between isolation by distance and isolation by resistance

### 2018-10-23 isolation_by_coalescence.tex
fixed merge repeats

\begin{figure}
\centering
    \includegraphics{figs/all_flat_divergences}
\caption{
    Comparison of mean coalescence times between samples and between replicates
    for a $4 \times 4$ discretization of a square landscape with uniform migration.
    Between the 16 geographic regions, there are 136 comparisons;
    these are shown for two nonoverlapping samples taken from three independent replicate simulations,
    each plotted against the mean value across all replicates.
    Colors denote simulation replicate,
    and point type (circle/triangle) denotes the sample.
    Without sampling or process noise, all points would fall on the $y=x$ line.
    Among the six sets of observations,
    simulation replicate explains 6.7\% of the variance,
    and spatial sampling explains 13.8\% of the variance.
    } \label{fig:h_val_comp}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/bias_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/bias_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/bias_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/bias_commute_dists}
\caption{
    \textbf{(Above:)} Posterior medians and \textbf{(below)} posterior distributions
    of of the inferred values of $g$ 
    for the $4 \times 4$ discretization 
    of the square landscape with biased migration,
    inferred with the
    \textbf{(left)} coalescence time-based,
    and \textbf{(right)} resistance distance-based method.
    Reverse time gene flow rates out of the bottom left section are very small,
    indicating that very few individuals living in that area of the landscape
    have ancestors from other regions of the graph.
    Most, but not all of the other gene flow rates are biased 
    in the direction we would expect.
    In the boxplots,
    black boxes show posterior distributions of gene flow rates down and to the left,
    and the adjacent green box corresponds to gene flow rate along the same edge
    in the opposite direction. 
    }
\label{fig:grid_bias_4x4_1}
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/barrier_locations}
    \includegraphics[width=0.45\textwidth]{figs/barrier_eems}
    \includegraphics[width=0.45\textwidth]{figs/barrier_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/barrier_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/barrier_commute_dists}
    \includegraphics[width=0.45\textwidth]{figs/barrier_coal_dists}
    \caption{
        Results from the \textbf{barrier} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using 
            \textbf{(middle left)} the commute time method and
            \textbf{(middle right)} the commute time method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the commute time method and
            \textbf{(bottom right)} the commute time method.
        \label{sfig:barrier_results}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/valley_locations}
    \includegraphics[width=0.45\textwidth]{figs/valley_eems}
    \includegraphics[width=0.45\textwidth]{figs/valley_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/valley_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/valley_commute_dists}
    \includegraphics[width=0.45\textwidth]{figs/valley_coal_dists}
    \caption{
        Results from the \textbf{valley} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using 
            \textbf{(middle left)} the commute time method and
            \textbf{(middle right)} the coalescent time method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the commute time method and
            \textbf{(bottom right)} the coalescent time method.
        \label{sfig:valley_results}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/expansion_locations}
    \includegraphics[width=0.45\textwidth]{figs/expansion_eems}
    \includegraphics[width=0.45\textwidth]{figs/expansion_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/expansion_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/expansion_commute_dists}
    \includegraphics[width=0.45\textwidth]{figs/expansion_coal_dists}
    \caption{
        Results from the \textbf{expansion} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using 
            \textbf{(middle left)} the commute time method and
            \textbf{(middle right)} the coalescence time method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the commute time method and
            \textbf{(bottom right)} the coalescence time method.
        \label{sfig:expansion_results}
    }
\end{figure}

>>>>

\begin{figure}
\centering
    \includegraphics{figs/all_flat_divergences}
\caption{
    Comparison of mean coalescence times between samples and between replicates
    for a $4 \times 4$ discretization of a square landscape with uniform migration.
    Between the 16 geographic regions, there are 136 comparisons;
    these are shown for two nonverlapping samples taken from three independent replicate simulations,
    each plotted against the the mean value across all replicates.
    Colors denote simulation replicate,
    and point type (circle/triangle) denotes the sample.
    Without sampling or process noise, all points would fall on the $y=x$ line.
    Among the six sets of observations,
    simulation replicate explains 6.7\% of the variance,
    and spatial sampling explains 13.8\% of the variance.
    } \label{fig:h_val_comp}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/bias_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/bias_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/bias_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/bias_commute_dists}
\caption{
    \textbf{(Above:)} Posterior medians and \textbf{(below)} posterior distributions
    of the inferred values of $g$ 
    for the $4 \times 4$ discretization 
    of the square landscape with biased migration,
    inferred with the
    \textbf{(left)} coalescence time-based,
    and \textbf{(right)} resistance distance-based method. 
    In the boxplots,
    black boxes show posterior distributions of gene flow rates up and to the right,
    and the adjacent green box corresponds to gene flow rate along the same edge
    in the opposite direction. 
    }
\label{fig:grid_bias_4x4_1}
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/barrier_locations}
    \includegraphics[width=0.45\textwidth]{figs/barrier_eems}
    \includegraphics[width=0.45\textwidth]{figs/barrier_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/barrier_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/barrier_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/barrier_commute_dists}
    \caption{
        Results from the \textbf{barrier} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using
            \textbf{(middle left)} the coalescence time method and
            \textbf{(middle right)} the the resistance distance method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the coalescence time method and
            \textbf{(bottom right)} the the resistance distance method.
        \label{sfig:barrier_results}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/valley_locations}
    \includegraphics[width=0.45\textwidth]{figs/valley_eems}
    \includegraphics[width=0.45\textwidth]{figs/valley_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/valley_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/valley_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/valley_commute_dists}
    \caption{
        Results from the \textbf{valley} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using 
            \textbf{(middle left)} the coalescence time method and
            \textbf{(middle right)} the the resistance distance method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the coalescence time method and
            \textbf{(bottom right)} the the resistance distance method.
        \label{sfig:valley_results}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=0.45\textwidth]{figs/expansion_locations}
    \includegraphics[width=0.45\textwidth]{figs/expansion_eems}
    \includegraphics[width=0.45\textwidth]{figs/expansion_coal_graph}
    \includegraphics[width=0.45\textwidth]{figs/expansion_commute_graph}
    \includegraphics[width=0.45\textwidth]{figs/expansion_coal_dists}
    \includegraphics[width=0.45\textwidth]{figs/expansion_commute_dists}
    \caption{
        Results from the \textbf{expansion} simulation:
        \textbf{(top left)} Positions of all individuals at the end of simulation.
        \textbf{(top right)} mean migration rates as estimated by EEMS.
        Below are shown
        posterior median migration rates 
            as estimated using 
            \textbf{(middle left)} the coalescence time method and
            \textbf{(middle right)} the the resistance distance method.
        Last are shown the posterior distributions, for
            \textbf{(bottom left)} the coalescence time method and
            \textbf{(bottom right)} the the resistance distance method.
        \label{sfig:expansion_results}
    }
\end{figure}
